### 2015-05-13 Draft/approach.tex
Removed unnecessary background

\textbf{POS Tags}: We first parse a sentence based on the function of POS tags. 
In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. 
For instance, consider the sentence which are then accurately annotated by the underlying NLP Parser:

@@

The Stanford parser finds it difficult to annotate accurately the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
As shown in Figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency. A catch all dependency is selected by a parser when no other appropriate dependency can be selected.
The \tool\ approach thus automatically break down the sentence into two smaller tractable sentences:

@@

\textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentences, this phase generates an intermediate (FOL) representation of the sentences. This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}. Figure~\ref{fig:FOLTree} is the FOL representation of the sentence  \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted''}. All the leaf nodes (entities) are represented as the bold words. For readability each node is appended with a number representing the in-order traversal index of the tree.

>>>>

{\small $\bullet$} \textbf{POS Tags}: We first parse a sentence based on the function of POS tags. 
In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. 
For instance, consider the sentence which are then accurately annotated by the underlying NLP Parser:

@@

The Stanford parser faces difficulty to annotate accurately the Stanford-typed dependencies of the sentence because of presence of various clauses acting on various subject-object pairs.
As shown in Figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency. A catch all dependency is selected by a parser when no other appropriate dependency can be selected.
The \tool\ approach thus automatically break down the sentence into two smaller tractable sentences:

@@

{\small $\bullet$} \textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentences, this phase generates an intermediate (FOL) representation of the sentences. This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}. Figure~\ref{fig:FOLTree} is the FOL representation of the sentence  \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted''}. All the leaf nodes (entities) are represented as the bold words. For readability each node is appended with a number representing the in-order traversal index of the tree.

### 2015-05-13 Draft/background.tex
Removed unnecessary background

\textit{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}: Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to.

\textit{Phrase and Clause Parsing}: Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking further enhances the syntax of a sentence in addition to POS tagging.

\textit{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}: The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks. The representation provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.

@@

\textit{Programming Keywords}~\cite{pandita12:inferring}: Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However POS tagging developed for well written news articles, often performs unsatisfactorily on domain-specific text.
In particular, with respect to API documents certain words have a different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

For instance, consider the word \CodeIn{POST}. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

@@

\textit{Lexical Token Reduction}~\cite{pandita13:WHYPER}:
The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
Thus, reduction in the number of lexical tokens greatly improves the accuracy of core NLP techniques. 
In particular, following heuristics have been used in related work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:
%These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.

\begin{itemize}

\item \textit{Period Handling}: Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.

@@

\textit{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}:
This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) like representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
Particularly, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this representation, by constructing an intermediate representation generator from semantically annotated sentences. 
The component is implemented as a sequence of cascading finite state machines based on the function of annotated Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

>>>>

{\small $\bullet$} \textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}: Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to.

{\small $\bullet$} \textbf{Phrase and Clause Parsing}: Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking further enhances the syntax of a sentence in addition to POS tagging.

{\small $\bullet$} \textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}: The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks. The representation provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.

@@

{\small $\bullet$} \textbf{Programming Keywords}~\cite{pandita12:inferring}: Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However POS tagging developed for well written news articles, often performs unsatisfactorily on domain-specific text.
In particular, with respect to API documents certain words have a different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

For instance, consider the word \CodeIn{POST}. 
The online Oxford dictionary %\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}}
has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

@@

{\small $\bullet$} \textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}:
The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
Thus, reduction in the number of lexical tokens greatly improves the accuracy of core NLP techniques. 
In particular, following heuristics have been used in related work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:
%These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.

%\item \textit{Period Handling}: Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
%Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
%The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.
\vspace*{-1.5ex}
\begin{itemize}

@@

{\small $\bullet$} \textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}:
This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) like representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
Particularly, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this representation, by constructing an intermediate representation generator from semantically annotated sentences. 
The component is implemented as a sequence of cascading finite state machines based on the function of annotated Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

### 2015-05-13 Draft/related.tex
Removed unnecessary background

\textbf{Formal Specification}:
Contracts formally specify the program behavior in terms of conditions that must hold before/after and/or during the execution of a method.
A significant amount of work has been done in automated inference of contracts.
Existing approaches use program analysis~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}
to automatically infer contracts.
However, studies~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA} demonstrate that a combination of developer-written and automatically extracted
contracts is the most effective approach for formally specifying the constraints on an API.

@@

\textbf{NLP in Software Engineering (SE)}:

Research advances~\cite{Marneffe08COLING,KleinNIPS03} in the accuracy of existing NLP techniques have inspired researchers and practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt and(/or) apply NLP techniques to solve problems in SE domain. 
Tan et al.~\cite{TanSOSP07} were the first to apply ML and NLP on code comments to detect mismatches between the comments and the implementation.
They rely on predefined rule templates targeted towards threading and lock related comments, and then apply ML-based approach to find comments following such rules.
The constraints inferred by their approach are the restrictions imposed by the developer on the client code.
In comparison, the temporal constraints inferred by \tool\ are the restriction imposed by the API library being used by the client code.

@@

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases. In contrast, the \tool\ approach works with API documents.
Pandita et al.~\cite{pandita12:inferring} proposed an NLP-based approach on inferring parameter constraints from method descriptions in the API documents. \tool\ differs from their work as follows.
\tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach. \tool\ significantly extends the infrastructure used by Pandita et al.~\cite{pandita12:inferring} in following dimensions.
First, \tool\ relies on ML to identify the temporal constraint sentences. The lower frequency of occurrence of temporal constraint sentences in comparison to parameter constraint sentences, make them harder to detect.
Second, the \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

\textbf{Augmented Documentation}:
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the Eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, \tool\ both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.

>>>>

{\small $\bullet$} \textbf{Formal Specification}:
Contracts formally specify the program behavior in terms of conditions that must hold before/after and/or during the execution of a method.
A significant amount of work has been done in automated inference of contracts.
Existing approaches use program analysis~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}
to automatically infer contracts.
However, studies~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA} demonstrate that a combination of developer-written and automatically extracted
contracts is the most effective approach for formally specifying the constraints on an API.

@@

{\small $\bullet$} \textbf{NLP in Software Engineering (SE)}:
Research advances~\cite{Marneffe08COLING,KleinNIPS03} in the accuracy of existing NLP techniques have inspired researchers and practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt and(/or) apply NLP techniques to solve problems in SE domain. 
Tan et al.~\cite{TanSOSP07} were the first to apply ML and NLP on code comments to detect mismatches between the comments and the implementation.
They rely on predefined rule templates targeted towards threading and lock related comments, and then apply ML-based approach to find comments following such rules.
The constraints inferred by their approach are the restrictions imposed by the developer on the client code.
In comparison, the temporal constraints inferred by \tool\ are the restriction imposed by the API library being used by the client code.

@@

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases. In contrast, the \tool\ approach works with API documents.
Our previous work~\cite{pandita12:inferring} proposed an NLP-based approach on inferring parameter constraints from method descriptions in the API documents. \tool\ differs from previous work as follows.
\tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach. \tool\ significantly extends the infrastructure in following dimensions.
First, \tool\ relies on ML to identify the temporal constraint sentences. The lower frequency of occurrence of temporal constraint sentences in comparison to parameter constraint sentences, make them harder to detect.
Second, the \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

{\small $\bullet$} \textbf{Augmented Documentation}:
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse IDE based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the Eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, \tool\ both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
